---
title: "Embedded Implicature"
author: "Mike Frank, Dan Lassiter, Chris Potts"
date: "August 21, 2014"
output: html_document
---

Preliminaries.

```{r}
rm(list=ls())
source("~/Projects/R/Ranalysis/useful_dplyr.R")
```

Read in data.

```{r}
setwd("~/Projects/embedded_implicature/Pragmatics-of-embedded-implicature/")
d <- read.csv("data/basketball-pilot-2-11-14-results-parsed.csv")
tt <- read.csv("data/trial_types.csv")
```

Filter out the training trials.

```{r}
d <- subset(d,is.na(trainingCorrect))
d$condition <- factor(d$condition)
```

Annoying releveling of factors so that everything looks nice on plots.

```{r}
d$quant1 <- NA
d$quant1[grepl("Every",d$sentence)] <- "Every"
d$quant1[grepl("Exactly one",d$sentence)] <- "Exactly one"
d$quant1[grepl("No",d$sentence)] <- "No"
d$quant1 <- factor(d$quant1,levels=c("No","Exactly one","Every"))

d$quant2 <- NA
d$quant2[grepl("none",d$sentence)] <- "None"
d$quant2[grepl("some",d$sentence)] <- "Some"
d$quant2[grepl("all",d$sentence)] <- "All"
d$quant2 <- factor(d$quant2,levels=c("None","Some","All"))

d$condition <- revalue(d$condition,
                       c("none-none-none"="NNN",
                         "none-none-half"="NNS",
                         "none-none-all"="NNA",
                         "none-half-half"="NSS",
                         "none-half-all"="NSA",                         
                         "none-all-all"="NAA",
                         "half-half-half"="SSS",
                         "half-half-all"="SSA",
                         "half-all-all"="SAA",
                         "all-all-all"="AAA"))  
d$condition <- factor(d$condition, levels=c("NNN",
                                      "NNS",
                                      "NNA",
                                      "NSS",
                                      "NSA",
                                      "NAA",
                                      "SSS",
                                      "SSA",
                                      "SAA",
                                      "AAA"))          
```

Merge in independent truth value judgments on each sentence (from Chris and Dan).  Not a necessary step, but useful for coloring graph. 

```{r}
dtt <- merge(d,tt)
dtt$truth <- dtt$truth.chris==1 & dtt$truth.dan==1
```

Analysis
----

Aggregate data, first within and then across participants.

```{r}
ms <- dtt %>% 
  filter(trial.type=="target") %>%
  group_by(condition, sentence, trial.type, quant1, quant2, truth, workerid) %>%
  summarise(response = mean(response)) %>%
  group_by(condition, sentence, trial.type, quant1, quant2, truth, add=FALSE) %>%
  summarise(n = n(), 
            cih = ci.high(response), 
            cil = ci.low(response), 
            response = mean(response))
    
```

Plot the main condition plot with likert means.

```{r}
quartz()
ggplot(ms,
       aes(x=condition, y=response, fill=truth, ymin=response-cil,
           ymax=response+cih)) + 
  geom_bar(stat="identity") + 
  geom_linerange() +
  scale_y_continuous(breaks=c(1,3,5,7)) + 
  facet_grid(quant1~quant2) + 
  geom_text(aes(x=5.5,y=7,label=sentence),hjust=.5,cex=3) +
  theme(axis.text.x = element_text(angle = 90,vjust=0.5))
```

Response distribution analysis
----

Histogram of all responses.

```{r}
quartz()
qplot(response, breaks=seq(.5,7.5,1),
      data=subset(dtt, trial.type == "target")) + 
  xlim(c(.5,7.5))
```

Here's a proposal: try discretizing the responses and redoing the analysis. 

```{r}
quartz()
msd <- dtt %>% 
  filter(trial.type=="target") %>%
  group_by(condition, sentence, trial.type, quant1, quant2, truth, workerid) %>%
  summarise(response = mean(response > 4)) %>%
  group_by(condition, sentence, trial.type, quant1, quant2, truth, add=FALSE) %>%
  summarise(n = n(), 
            cih = ci.high(response), 
            cil = ci.low(response), 
            response = mean(response))

ggplot(msd,
       aes(x=condition, y=response, fill=truth, ymin=response-cil,
           ymax=response+cih)) + 
  geom_bar(stat="identity") + 
  geom_linerange() +
  facet_grid(quant1~quant2) + 
  ylim(c(0,1)) +
  geom_text(aes(x=5.5,y=1,label=sentence),hjust=.5,cex=3) +
  theme(axis.text.x = element_text(angle = 90,vjust=0.5))
```

Histograms for key conditions
----

Histogram of likert scale usage for key condition, C&S Experiment 2. "Exactly one player hit some of his shots."

```{r}
qplot(response,facets=.~condition, binwidth=1,
      data=subset(dtt,trial.type=="target" &
                  sentence=="Exactly one player hit some of his shots")) + 
  scale_x_continuous(breaks=c(1,3,5,7))
```

And for "no ... none":

```{r}
qplot(response,facets=.~condition,binwidth=1,
      data=subset(dtt,trial.type=="target" &
                    sentence=="No player hit none of his shots"))
```

And for "Every  ... some" (C&S Experiment 1):

```{r}
qplot(response,facets=.~condition,binwidth=1,
      data=subset(dtt,trial.type=="target" &
                    sentence=="Every player hit some of his shots"))
```

Now for the key "some" column of the larger plot. 

```{r}
qplot(response,facets=quant1~condition,binwidth=1,
      data=subset(dtt,trial.type=="target" &
                    quant2=="Some"))
```