---
title: "Goal manipulations and their effect on embedded implicature"
author: "Mike Frank, Dan Lassiter, Chris Potts"
date: "October 15, 2014"
output: pdf_document
---

Preliminaries.

```{r, echo=TRUE}
rm(list=ls())
source("~/Projects/R/Ranalysis/useful_dplyr.R")
setwd("~/Projects/R/embed_ball")
library(knitr)
opts_chunk$set(cache=TRUE, echo=TRUE, message=FALSE, warning=FALSE, error=FALSE) 
```

Now read and bind data.

```{r}
d1 <- read.csv("data/basketball-goal-manip-e2.csv")
d2 <- read.csv("data/basketball-goal-manip-e2-evening.csv")
tt <- read.csv("data/trial_types.csv")
d <- rbind(d2,d1)
```

Filter training trials and repeat participants. (Assumes ordering is chronological: FIXME). 

```{r}
length(d$workerid)
length(unique(d$workerid))

d <- d %>% filter(is.na(trainingCorrect)) # training
d$condition <- factor(d$condition) # drop levels
length(d$workerid)
length(unique(d$workerid))

d <- d %>% filter(grepl("ngl|NGL",language)) # language
length(d$workerid)
length(unique(d$workerid))

d <- d %>% # first instance of worker 
  group_by(workerid, trialnum) %>% 
  filter(row_number(rt) == 1)  # doesn't matter which row
length(d$workerid)
length(unique(d$workerid))
```

Boring releveling. 

```{r}
d$quant1 <- NA
d$quant1[grepl("Every",d$sentence)] <- "Every"
d$quant1[grepl("Exactly one",d$sentence)] <- "Exactly one"
d$quant1[grepl("No",d$sentence)] <- "No"
d$quant1 <- factor(d$quant1,levels=c("No","Exactly one","Every"))

d$quant2 <- NA
d$quant2[grepl("none",d$sentence)] <- "None"
d$quant2[grepl("some",d$sentence)] <- "Some"
d$quant2[grepl("all",d$sentence)] <- "All"
d$quant2 <- factor(d$quant2,levels=c("None","Some","All"))

d$condition <- revalue(d$condition,
                       c("none-none-none"="NNN",
                         "none-none-half"="NNS",
                         "none-none-all"="NNA",
                         "none-half-half"="NSS",
                         "none-half-all"="NSA",                         
                         "none-all-all"="NAA",
                         "half-half-half"="SSS",
                         "half-half-all"="SSA",
                         "half-all-all"="SAA",
                         "all-all-all"="AAA"))  
d$condition <- factor(d$condition, levels=c("NNN",
                                      "NNS",
                                      "NNA",
                                      "NSS",
                                      "NSA",
                                      "NAA",
                                      "SSS",
                                      "SSA",
                                      "SAA",
                                      "AAA"))     

```

Now merge in the truth value judgments.

```{r}
dtt <- left_join(d,tt)
dtt <- tbl_df(dtt)
dtt$truth <- dtt$truth.chris==1 & dtt$truth.dan==1
```

And filter by RT and correctness. 30s is like M + 3SD or so. 

```{r}
mean(dtt$advancesCorrectFirstTime == "yes")
mean(dtt$rt)
sd(dtt$rt)
mean(dtt$rt > 30000)

dtt <- dtt %>% filter(advancesCorrectFirstTime == "yes", 
                      rt < 30000)
```

And aggregate. 

```{r}
ms <- dtt %>% 
  filter(trial.type=="target") %>%
  group_by(tournamentCondition, condition, quant1, quant2, 
           sentence, workerid) %>%
  summarise(response = mean(response)) %>%
  ungroup() %>%
  group_by(tournamentCondition, condition, 
           quant1, quant2, sentence) %>%
  summarise(cih = ci.high(response),
            cil = ci.low(response), 
            response = mean(response),
            n = length(response)) 
```

Now plot:

```{r, fig.width=10}
ggplot(ms,
       aes(x=condition, y=response, fill=tournamentCondition,
           ymin=response-cil, ymax=response+cih)) + 
  geom_bar(stat="identity", position=position_dodge(width=.9)) + 
  geom_linerange(position=position_dodge(width=.9)) +
  ylim(c(0,7)) +
  facet_grid(quant1~quant2) + 
  geom_text(aes(x=5.5,y=7,label=sentence),hjust=.5,cex=3) +
  theme(axis.text.x = element_text(angle = 90,vjust=0.5))
```

Some cursory t-tests for comparisons of interest. 

```{r}
t.test(subset(dtt,tournamentCondition=="any advances" & 
                quant1=="Every" & quant2=="Some" & condition=="AAA")$response,
       subset(dtt,tournamentCondition=="all advances" & 
                quant1=="Every" & quant2=="Some" & condition=="AAA")$response)


t.test(subset(dtt,tournamentCondition=="any advances" & 
                quant1=="Exactly one" & quant2=="Some" & condition=="NNA")$response,
       subset(dtt,tournamentCondition=="all advances" & 
                quant1=="Exactly one" & quant2=="Some" & condition=="NNA")$response)

t.test(subset(dtt,tournamentCondition=="any advances" & 
                quant1=="No" & quant2=="Some" & condition=="NAA")$response,
       subset(dtt,tournamentCondition=="all advances" & 
                quant1=="No" & quant2=="Some" & condition=="NAA")$response)
```

Non-parametrics:

```{r}
wilcox.test(subset(dtt,tournamentCondition=="any advances" & 
                quant1=="Every" & quant2=="Some" & condition=="AAA")$response,
       subset(dtt,tournamentCondition=="all advances" & 
                quant1=="Every" & quant2=="Some" & condition=="AAA")$response)

wilcox.test(subset(dtt,tournamentCondition=="any advances" & 
                quant1=="Exactly one" & quant2=="Some" & condition=="NNA")$response,
       subset(dtt,tournamentCondition=="all advances" & 
                quant1=="Exactly one" & quant2=="Some" & condition=="NNA")$response)

wilcox.test(subset(dtt,tournamentCondition=="any advances" & 
                quant1=="Exactly one" & quant2=="Some" & condition=="SAA")$response,
       subset(dtt,tournamentCondition=="all advances" & 
                quant1=="Exactly one" & quant2=="Some" & condition=="SAA")$response)
```

Graph distributional differences. First, Every... some. AAA

```{r}
ss <- dtt %>% 
  filter(quant1=="Every" & quant2=="Some" & condition=="AAA")

qplot(response, fill=tournamentCondition, 
      position="dodge", binwidth=1,
      data=ss) + 
  scale_x_continuous(lim=c(1,8),breaks=c(1,3,5,7))
```

Now, Exactly one... some. NNA

```{r}
ss <- dtt %>% 
  filter(quant1=="Exactly one" & quant2=="Some" & condition=="NNA")

qplot(response, fill=tournamentCondition, 
      position="dodge", binwidth=1,
      data=ss) + 
  scale_x_continuous(lim=c(1,8),breaks=c(1,3,5,7))
```

Now, Exactly one... some. SAA

```{r}
ss <- dtt %>% 
  filter(quant1=="Exactly one" & quant2=="Some" & condition=="SAA")

qplot(response, fill=tournamentCondition, 
      position="dodge", binwidth=1,
      data=ss) + 
  scale_x_continuous(lim=c(1,8),breaks=c(1,3,5,7))
```

Now, Exactly one... some. NSA

```{r}
ss <- dtt %>% 
  filter(quant1=="Exactly one" & quant2=="Some" & condition=="NSA")

qplot(response, fill=tournamentCondition, 
      position="dodge", binwidth=1,
      data=ss) + 
  scale_x_continuous(lim=c(1,8),breaks=c(1,3,5,7))
```